Source Summaries

### 2020-02-22 paper/sourceSummaries/summary4.tex
prepped for the future summaries
added my section and updated future files
Added citation
Added summary 4

\section{Summary 3}

@@

\noindent
Member name

@@

\pagebreak

>>>>

\section{Summary 4}

@@

\noindent
Daniel Capps

@@

\noindent
\subsection{An Active Man-in-the-Middle Attack on Bluetooth Devices}

\noindent
Connor Leavesley

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{BluetoothMITMTal}

\noindent
The author looks to outline the main issues with BLE security. He focus on a possible architecture for a man-in-the-middle attack and a case study on a MITM'd device and an associated application.

\noindent
The author is utilizing Game Theory. He is attacking a Bluetooth connection via a MITM.

\noindent
The author uses a Dax-Hub SW-28 Smart Bracelet and its associated app PowerSensor and the subject of the MITM attack. He used Kali Linux as the attacker and installed GATTacker and BtleJuice. He connected a CSR 4.0 dongle to a VM to transmit data between the app, the bracelet, and the middleman. He then uses GATTacker to intercept the BLE advertisements and copy the GATT profile of the bracelet. The author uses the GATT to simulate the device. Tal was then able to send fake to the device.

\noindent
The author found that it was far to easy to intercept device communications and take control. Due to the inherent insecurities of the BLE protocol, he was able to change data that the device displayed, as well as take control of mobile camera via the app.

\noindent
The author does not give any ideas as to future directions. The security issues with BLE are widely know, and Tal hopes to explain the security issues here and how to exploit them in a unique manner.

\noindent
Joshua Niemann

\noindent
Jacob Ruud

\noindent
Quintin Walters

\Urlmuskip=0mu plus 1mu\relax
\pagebreak
